---
title: "Infostop"
author: ""
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Infostop}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

# Infostop

This vignette demonstrates the two-stage Infostop workflow in R. The first
stage identifies stationary events (`identify_stops()`), and the second stage
groups nearby events into recurring sites (`identify_sites()`).

## Setup

```{r setup}
library("trackframe")
library("infostop")

data("path_trackframe", package = "trackframe")
head(path_trackframe)
```


## Identify stops and sites

```{r identify}
stops <- identify_stops(path_trackframe)
sites <- identify_sites(stops)

head(stops$stop_id)
head(sites$site_id)
```

`NA` labels represent points that are not assigned to a stop or site.

The main parameters can be changed independently for the two stages:

```{r parameters}
stops <- identify_stops(
  path_trackframe,
  r1 = 10,
  min_size = 2L,
  min_staying_time = 300
)

sites <- identify_sites(
  stops,
  r2 = 10,
  label_singleton = TRUE,
  weighted = FALSE
)
```

## Centers

Stop centers are median coordinates of the points belonging to each stop.
Site centers are computed from the stop centers belonging to each site.

```{r centers}
stop_centers(stops)
site_centers(sites)
```

## Intervals

`compute_intervals()` summarizes consecutive periods with the same site label.
The time column is converted to integer seconds for this example.

```{r intervals}
intervals <- compute_intervals(
  labels = sites$site_id,
  times = as.integer(sites[["time"]]),
  max_time_between = 86400
)

head(intervals)
```

## Multiple tracks

The same workflow can process multiple track IDs. Each track is clustered
independently and the resulting labels are returned in the original track
order.

```{r multiple-tracks}
data("paths_trackframe", package = "trackframe")

stops_multiple <- identify_stops(paths_trackframe)
sites_multiple <- identify_sites(stops_multiple)

length(sites_multiple$site_id)
head(sites_multiple$site_id)
```
