---
title: "Infostop"
author: ""
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Infostop}
  %\VignetteEngine{knitr::knitr}
editor_options: 
  chunk_output_type: console
---

# Infostop Vignette

This vignette demonstrates how to use `infostop`.

# Load package and initialize infostop

```{r}
library("trackframe")
library("infostop")

infostop_initialize()
```


## sftrack

### Onestep approach

```{r}
data("path_sftrack", package = "trackframe")
head(path_sftrack)
class(path_sftrack)

infostop <- infostop(data = path_sftrack,
                     distance_metric = "haversine")

head(infostop$labels, n=20)
head(infostop$compute_label_medians())
```

### Twostep approach

```{r}
data("path_sftrack", package = "trackframe")

identify_stops_sftrack <- identify_stops(data = path_sftrack,
                            distance_metric = "haversine")
clusters_sftrack <- identify_sites(identify_stops_sftrack$stop_events, distance_metric = "haversine")
two_step_labels_sftrack <- match_labels(clusters_sftrack, identify_stops_sftrack$event_map)

#compare with onestep approach
infostop_sftrack <- infostop(data = path_sftrack,
                        distance_metric = "haversine")
all.equal(two_step_labels_sftrack, infostop_sftrack$labels)
```

## move2

```{r}
data("path_move2", package = "trackframe")
head(path_move2)
class(path_move2)

infostop <- infostop(data = path_move2,
                     distance_metric = "haversine")

head(infostop$labels, n=20)
head(infostop$compute_label_medians())
```


## `matrix` or `data.frame`

When applying infostop to `matrix` or `data.frame` objects, one has two options:

- Coerce to an object of class `trackframe` by applying `as.trackframe()`
- specify `x`, `y` and `t` column explicitly in `infostop_xyt()`

### Coerce to `trackframe`

As objects of class `trackframe` always have easting/northing coordinates, `distance_metric` needs to be `"euclidean"`.

```{r}
data("path_data_frame", package = "trackframe")
head(path_data_frame)
class(path_data_frame)
path_tf <- as.trackframe(path_data_frame, crs_input = 4326)
class(path_tf)
head(path_tf)
attr(path_tf, "easting")
attr(path_tf, "northing")
# need to use euclidean distance as coordinates were transformed to easting/northing
infostop_df <- infostop(data = path_tf,
                       distance_metric = "euclidean")
```


### `infostop_xyt()`


```{r}
data("path_matrix", package = "trackframe")
head(path_matrix)
class(path_matrix)
infostop_xyt <- infostop_xyt(x = path_matrix[, "longitude"],
                             y = path_matrix[, "latitude"],
                             t = path_matrix[, "time"],
                             distance_metric = "haversine")

```


## Run `infostop` with objects of class `trackframe`

As objects of class `trackframe` always have easting/northing coordinates, `distance_metric` needs to be `"euclidean"`.

```{r}
data("path_trackframe", package = "trackframe")
head(path_trackframe)

infostop <- infostop(data = path_trackframe,
                     distance_metric = "euclidean")
```

To obtain the labels of the stop locations,
```{r}
head(infostop$labels, n=20)
```
can be used.
For each stop location (identified by a label), we can compute the median coordinates using
the `compute_label_medians()` method:
```{r}
head(infostop$compute_label_medians())
```


### multiple IDs

```{r}
data("paths_trackframe", package = "trackframe")
head(paths_trackframe)
unique(paths_trackframe$id)

infostop <- infostop(data = paths_trackframe,
                     distance_metric = "euclidean")
length(infostop$labels)

tf1 <- split_by_id(paths_trackframe)[[1]]
infostop_mtf1 <- infostop(data = tf1,
                         distance_metric = "euclidean")
```
